A Domain Specific Language for SpectreGuard

### 2020-12-06 paper/main.tex
Analysis section and more complex example

\section{Examples}

@@

\section{Information Flow Analysis}
\label{sec:Analysis}
\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
    }
    {%
      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
    }\\
    \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
    {%
      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash v \in L(\ttt{x})
    }
    {%
      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
\end{gather*}
\end{minipage}}
  \caption{Information flow analysis rules which define the relation $\sarr$}
\label{fig:FlowRules}
\end{figure}
...

>>>>

\section{Examples}
\label{sec:Examples}

@@

\section{Information Flow Analysis}
\label{sec:Analysis}

In Section \ref{sec:Examples}, a significant limitation of the sensitivity type checking
was outlined. In this section we address this limitation using a static analysis technique.
Possible leaks from secret variables to public variables via control flow constructs will
be analyzed and the results of this analysis will be described in the form of
a forest of trees, given in DOT format (which can then be converted to other formats,
such as PDF)~\cite{DOT}. The C code generated from \ttt{example4} is shown in Fig. \ref{fig:GenC4}.
Note that the secret array is named \verb|_fs_0| and the public array is named \verb|_fs_1| by the
code generator. From the original \ttt{example4}, the information flow analyzer generates the
graph given in Fig. \ref{fig:Analysis4}. Secret variables are represented as nodes with
a rectangular shape and public variables are represented as nodes with an elliptic shape. An
arrow going from one node to another represents a possible information leak from the first
node to the second node due to a control flow construct.

\begin{figure}[h]
\begin{lstlisting}{language=C}
int* _fs_0[8] __attribute__((nospec))__;
int* _fs_1[8];
for (int _fs_2 = 0; _fs_2 < 8; _fs_2 = _fs_2 + 1) {
  int _fs_3 = 0;
  for (int _fs_4 __attribute__((nospec))__ = 0;
       _fs_4 < (_fs_0[_fs_2]);
       _fs_4 = _fs_4 + 1) {
    _fs_3 = _fs_3 + 1;
  }
  _fs_1[_fs_2] = _fs_3;
}
\end{lstlisting}
\caption{C code generated from \ttt{example4}}
\label{fig:GenC4}
\end{figure}

\begin{figure}[h]
\centering
  \resizebox{0.3\columnwidth}{4cm}{\includegraphics{Diagrams/example4-analysis.pdf}}
\caption{Results of leak analysis on \ttt{example4}}
\label{fig:Analysis4}
\end{figure}

A more complicated example is \ttt{example6} in the following:

\begin{lstlisting}[language=Haskell]
example5 :: Cmd ()
example5 = do
  secretArray <- allocSecret @Int 8
  publicArray <- allocPublic @Int 8

  for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do

    leak <- decl (0 :: Int)

    for (0 :: Expr Secret Int) (\j -> ((j <? (secretArray ! i))
                                      ,(j += 1)
                                      ,do
      leak += 1
      ))
    (publicArray ! i) .= leak
    ))

  secretArrayA <- allocSecret @Int 8
  secretArrayB <- allocSecret @Int 8
  publicArray2 <- allocPublic @Int 8

  secretArrayA .= secretArray
  secretArrayB .= secretArrayA

  for (0 :: Expr Public Int) (\i -> ((i <? 8), (i += 1), do

    leak2 <- decl (0 :: Int)

    for (0 :: Expr Secret Int) (\j -> ((j <? (secretArrayB ! i))
                                      ,(j += 1)
                                      ,do
      leak2 += 1
      ))
    (publicArray2 ! i) .= leak2
    ))
\end{lstlisting}

In the generated code for \ttt{example5}, we have the correspondence between variables in the EDSL code and the
generated C code given in the table in TABLE \ref{table:Names5}. As both the C code generator and the
static analysis tool use the same name generator, these names stay stable across the results of both. The analysis of \ttt{example5} is given in Fig. \ref{fig:Analysis5}.

\begin{table}[h]
  \centering
  \begin{tabular}{|c|c|}
    \hline
    EDSL name & Generated C Name \\
    \hline
    \verb|secretArray| & \verb|_fs_0|\\
    \verb|publicArray| & \verb|_fs_1|\\
    \verb|leak| & \verb|_fs_3|\\
    \verb|secretArrayA| & \verb|_fs_5|\\
    \verb|secretArrayB| & \verb|_fs_6|\\
    \verb|publicArray2| & \verb|_fs_7|\\
    \verb|leak2| & \verb|_fs_9|\\
    \hline
  \end{tabular}
\caption{Correspondence between EDSL names and generated C names for \ttt{example5}}
\label{table:Names5}
\end{table}

\begin{figure}[h]
\centering
  \resizebox{0.3\columnwidth}{4cm}{\includegraphics{Diagrams/example5-analysis.pdf}}
\caption{Results of leak analysis on \ttt{example5}}
\label{fig:Analysis5}
\end{figure}

\begin{figure}[h]
  \centering
\resizebox{0.68\linewidth}{!}{
\begin{minipage}{\linewidth}
  \centering
\begin{gather*}
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: Expr Public $\tau$ $\rarr$ Cmd $\alpha$}
    \\ \Delta;\Gamma\vdash A(\ttt{decl v >>= ($\lambda$x $\rarr$ k)})
    }
    {%
      \Delta,Pub(x);\Gamma \vdash A(\ttt{k})
    }\\
    \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{x :: Expr Public $\tau$}
    & \Delta;\Gamma \vdash \ttt{y :: Expr Public $\tau$}
    \\ \Delta;\Gamma \vdash \ttt{k :: () $\rarr$ Cmd $\alpha$}
    & \Delta;\Gamma \vdash A(\ttt{(x .= y) >>= k})
    \\ \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
    {%
      \Delta;\Gamma \vdash \ttt{x} \sarr L(\ttt{x})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    & \Delta;\Gamma \vdash \ttt{body :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{while cond body})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{body})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{t})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash \ttt{cond :: Expr Bool}
    \\ \Delta;\Gamma \vdash \ttt{t :: Cmd $\alpha$}
    & \Delta;\Gamma \vdash \ttt{f :: Cmd $\alpha$}
    \\ \Delta;\Gamma \vdash A(\ttt{if cond t f})
    & \Delta;\Gamma \vdash s \in Secrets(\ttt{cond})
    \\ \Delta;\Gamma \vdash Pub(\ttt{x})
    }
    {%
      \Delta, s \in L(\ttt{x});\Gamma \vdash A(\ttt{f})
    }\\
  \\
  \inference{%
    \Delta;\Gamma \vdash v \in L(\ttt{x})
    }
    {%
      \Delta;\Gamma \vdash L(\ttt{x}) \neq \varnothing
    }
\end{gather*}
\end{minipage}}
  \caption{Information flow analysis rules which define the relation $\sarr$}
\label{fig:FlowRules}
\end{figure}
...
